---
title: "Efficent DA Project 2 2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## GitHub Documents
###Guided project to get acquinted with dataset, do data cleaning and analyze it.
##As data analysis for company that sells books for learning programming.  Company wants
##us to check out sales data and see if we can extract any useful information from it.
#Inported dataset using readr book review...
#how big is the data set?

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r book_review}
dim(book_reviews)
#number of rows in data set use nrow
nrow(book_reviews)
#2000
#number of columns in data set
ncol(book_reviews)
#4
#first 10 rows the head
head(book_reviews, n = 10)
#last 10 rows the tail
tail(book_reviews, n = 10)
#to get structure of DF or vector
str(book_reviews)
#Three columns of charater values and one of numbers the price
#look at the summary breakdown of distribution for price mainly
summary(book_reviews)
#use glimpse function also provide good look at dataset
glimpse(book_reviews)
#What are the column names?
colnames(book_reviews)
```

#book colunm represents name of the book Character values
#review column represents a rating of the book Character values
#State represents where book was sold Character values
#price respresents how much the book sold for number/double values
#Need to use iteration or for loop to figure out types of columns


```{r}
for (c in colnames(book_reviews)){
  typeof(book_reviews[[c]])
}
#What are unique values in each column?
for (c in colnames(book_reviews)){
  print("unique values in column are:")
  print (c)
  print(unique(book_reviews[[c]]))
  print("")
}
#remove all the NAs from the rows as this is useless and we dont know imputation yet
filtered_review = book_reviews %>%
    filter(!is.na(review))
  
dim(filtered_review)
```


```
#results removed 206 rows that contained NA in review column.  1794 rows now
#removing 200 lines of data could effect overall results should learn imputation

#now need to get State column correct with states having two forms long and #abreviated
#State data has the following information CA and California, NY and New York
#FL and Florida and TX and Texas the four most pop states in USA
#Create a new column clean_state using mutate() function with all state #abreviations.
#bring in stringr toolset
#Note that the `echo = FALSE` parameter was added to the code chunk to prevent #printing of the R code that generated the plot.

```{r}
install.packages("stringr")
clean_review <- filtered_review %>%
  mutate(
    state = case_when(
      state == "California" ~ "CA",
      state == "New York" ~ "NY",
      state == "Texas" ~ "TX",
      state == "Florida" ~ "FL",
      TRUE ~ state #ignore case where it is already postal code
  )
    )
```

#now focus on converting review choices into numeric form Need to convert #following
# poor = 1, fair = 2, good = 3, great = 4 and exellent = 5 create column #review_num
#create a new column to determine if score was high or not called is_high_review
#for exercise 4 or higher qualifies as high score
#it is TRUE if reveiw num is 4 or greater and false otherwise

```{r}
tidy_review <- clean_review %>%
  mutate(
    review_num = case_when(
      review == "Poor" ~ "1",
      review == "Fair" ~ "2",
      review == "Good" ~ "3",
      review == "Great" ~ "4",
      TRUE ~ "5"#new column reveiw_num created coverting to numbers
      ),
    is_high_review  = if_else(
      review_num >= "4" ,TRUE , FALSE) 
  )
```

#new colunm is_high_review created with true value for high reveiw rating
#Now we start data anyalysis with clean dataset called tidy_review
#want to find out what book is most profitable??????
#most profitable could mean book purchased the most...
#could also mean how much money did each book generate.
#I am focus on total count of book titles for popularity
#need to try SPLIT Apply Combine Workflow to create function to count titles in #book column

```{r}
summary_count_book <- tidy_review %>%
  group_by(book) %>%
  summarize(
    count = n()
  ) %>%
  arrange(-count)
```

#Report For Project 2 in Dataquest
#
#
#Introduction
#
#I am working this data analysis project to improve my data analysis skills.
#The data provided consisted of 2000 rows and 4 columns of information.  One #column 
#consisted of double numeric data and the other 3 consisted of character data.
#In this project I went though the process of understanding the data, cleaning the #data
#figuring out which book was most profitable backed by anyalysis.  As just stated
#My job was to answer the question of which book is the most profitable.
#
#
#Findings
#
#Prior to answering the key question, The data had to be cleaned.  This included finding
#unique values in each column, remove all the NAs from the dataset reducing the dataset
#to 1794 rows of information, Standardizing the state column to reflect state intials
#convert word ratings into numeric ratings and decide that 4 and above are good rating
#based on my experiences.
#
#
#Conclusion
#
#I chose profitability to mean the book that sold the most.  In the case of my 
#analysis, Fundamentals of R for beginners book has highest total of all five 
#but not by much as all five are between 352 and 366...




